Ethereum: Un Registro Generico delle Transazioni Sicuro e Decentralizzato \\ {\smaller \textbf{Final Draft - UNDER REVIEW}}

### 2016-02-03 Paper.tex
Update Paper.tex

There are number of intrinsic parameters used when creating an account: sender ($s$), original transactor ($o$), available gas ($g$), gas price ($p$), endowment ($v$) together with an arbitrary length byte array, $\mathbf{i}$, the initialisation EVM code and finally the present depth of the message-call/contract-creation stack ($e$).

We define the creation function formally as the function $\Lambda$, which evaluates from these values, together with the state $\boldsymbol{\sigma}$ to the tuple containing the new state, remaining gas and accrued transaction substate $(\boldsymbol{\sigma}', g', A)$, as in section \ref{ch:transactions}:
\begin{equation}
(\boldsymbol{\sigma}', g', A) \equiv \Lambda(\boldsymbol{\sigma}, s, o, g, p, v, \mathbf{i}, e)
\end{equation}

The address of the new account is defined as being the rightmost 160 bits of the Keccak hash of RLP encoding of the structure containing only the sender and the nonce. Thus we define the resultant address for the new account $a$:
\begin{equation}
a \equiv \mathcal{B}_{96..255}\Big(\mathtt{\tiny KEC}\Big(\mathtt{\tiny RLP}\big(\;(s, \boldsymbol{\sigma}[s]_n - 1)\;\big)\Big)\Big)
\end{equation}

where $\mathtt{\tiny KEC}$ is the Keccak 256-bit hash function, $\mathtt{\tiny RLP}$ is the RLP encoding function, $\mathcal{B}_{a..b}(X)$ evaluates to binary value containing the bits of indices in the range $[a, b]$ of the binary data $X$ and $\boldsymbol{\sigma}[x]$ is the address state of $x$ or $\varnothing$ if none exists. Note we use one fewer than the sender's nonce value; we assert that we have incremented the sender account's nonce prior to this call, and so the value used is the sender's nonce at the beginning of the responsible transaction or VM operation.

>>>>

C'è un numero di parametri intrinseci impiegati quando viene creato un account: mittente ($s$), colui che effettua per primo la transazione ($o$), gas disponibile ($g$), prezzo del gas ($p$), dotazione ($v$) insieme con un insieme di dati di lungherzza arbitraria, $\mathbf{i}$, il codice EVM di inizializzazione ed infine la profondità attuale dello stack del messaggio di chiamata/creazione del contratto ($e$).

Definiamo la funzione di creazione formalmente come la funzione $\Lambda$, che fa una stima da questi valori, insieme con lo stato $\boldsymbol{\sigma}$ verso l'insieme di dati che contiene il nuovo stato, il restante gas e il maturato sottotostato della transazione $(\boldsymbol{\sigma}', g', A)$, come in sezione \ref{ch:transactions}:
\begin{equation}
(\boldsymbol{\sigma}', g', A) \equiv \Lambda(\boldsymbol{\sigma}, s, o, g, p, v, \mathbf{i}, e)
\end{equation}

L'indirizzo del nuovo account è definito come essere più a festra di 160 bits dell'hash di Keccak della codifica RLP della struttura contenete solo il mittente ed il nonce. Perciò definiamo l'indirizzo risultante per il nuovo account $a$:
\begin{equation}
a \equiv \mathcal{B}_{96..255}\Big(\mathtt{\tiny KEC}\Big(\mathtt{\tiny RLP}\big(\;(s, \boldsymbol{\sigma}[s]_n - 1)\;\big)\Big)\Big)
\end{equation}

dove $\mathtt{\tiny KEC}$ è la funzione di hash Keccak 256-bit, $\mathtt{\tiny RLP}$ è la funzione di codifica RLP, $\mathcal{B}_{a..b}(X)$ stima il valore binario contenete i bit degli indici nel range $[a, b]$ dei dati binari $X$ and $\boldsymbol{\sigma}[x]$ è l'indirizzo stato di $x$ or $\varnothing$ se nessuno esiste. Si noti che impieghiamo un valore minore rispetto a quello del nonce del mittente; asseriamo che abbiamo incrementato il nonce dell'account del mittente prima di questa chiamata, e così il valore impiegato nel nonce del mittente all'inizio della transazione che ha dato inizio o dell'operazione VM.
